---
title: "Analysis of the distribution of predictions of the db aphid_TE_db_G0.db and aphid_TE_db_G1.db length"
output: html_document
author: "Kamély Lumière"
---



# Import ggplot library for tracing plots (option)

```{r}
library(ggplot2)
```



# Import the file list-length-G0.fa and the file list-length-G1.fa (Célia's files) which contains the length of all prediction of these db and their ids
```{r }

data_G0 <- read.table(file ="C:/Users/Anne-Flore/Desktop/klumiere/list-length_G0.txt", header = TRUE) #read the file from the path in our computer
#head(data_G0,5)
dim(data_G0)#dim de data_G0--> 106872 rows (each seq of TE) and 2 columns (id/length)


data_G1 <- read.table(file ="C:/Users/Anne-Flore/Desktop/klumiere/list-length_G1.txt", header = TRUE)
head(data_G1)
#head(data_G1)
dim(data_G1)#dim de data_G1--> 108481 rows (each seq of TE) and 2 columns (name=id/length)

```


# Extraction of all the values of length ( 2nd column of the file only) for each list of length of g0 et g1 with their ids (name)


```{r}

length_seq0<- data_G0[,2];  #list of all the length of the db_G0
idf_seq0<-data_G0[,1]; #list of all the ids of the db_G1
length(length_seq0)#verification of the total number od=f sequences-->106 872

t<-unique(length_seq0); #to know how many different size is there in the db_G0:3946
length(t)

min(length_seq0) #minimal length in db_G0 = 76
max(length_seq0) #maximal length in db_G0=214590


#same commands for the db_G1
length_seq1<- data_G1[,2]; 
idf_seq1<-data_G1[,1]
length(length_seq1)

s<-unique(length_seq1);
length(s)#3980 different size ind the db_G1

min(length_seq1) #minimal length in db_G1= 76
max(length_seq1) #maximal length in db_G1=214590


#dataframe with id (1rst col) and their length (2nd col) for g0 (df0) for db_G0 and db_G1
df0<-data.frame(idf_seq0,length_seq0);
df1<-data.frame(idf_seq1,length_seq1);


#to know how many sequences have a length<100 bp for each db
df0$length_seq0[df0$length_seq0<100]
df1$length_seq1[df1$length_seq1<100]

#to know how many sequences have a length=100 bp for each db
length(df0$length_seq0[df0$length_seq0==100])
length(df1$length_seq1[df1$length_seq1==100])


a<-table(length_seq0);a # to count for each size of the prediction in the db how many prediction have the size
#tail(a,1000)




```



# Plot of the distribution of the length of the predictions in the db_G0 and db_G1


```{r}

p0<-plot(table(df0$length_seq0), xlab="Length of G0 database predictions in pb", ylab="Number of sequences");p0 ### Have not  a good shape 
p1<-plot(table(df1$length_seq1), xlab="Length of G1 database predictions in pb", ylab="Number of sequences");p1

#to have the main informations about these distributions
summary(df0)
summary(df1)


#to get the ids of predictions with a length =148 pb in db_G0
#df0$idf_seq0[df0$length_seq0==148] 

```



# Plot with intervals for db_G0

```{r}

#to create interval in the length of prediction of db_G0
df0$length_seq0_i<-cut(df0$length_seq0,c(0,100,1000,10000,100000,300000),dig.lab = 10) #dig.lab => to remove the scientific writing and have the 0000...
#df0$length_seq0_i

summary(df0$length_seq0_i) #to show the main information about the distribution of length *with interval*

#barplots of the distribution of the length of prediction in the db_G0
bi0<-barplot(table(df0$length_seq0_i), xlab="Length of G0 database sequences in pb", ylab="Number of predictions");bi0 #display the barplot


```

# Plot with intervals for db_G1



```{r}
#to create interval in the length of prediction of db_G1
df1$length_seq1_i<-cut(df1$length_seq1,c(0,100,1000,10000,100000, 200000),na.rm=TRUE,dig.lab = 10)
#head(df1$length_seq1_i)
summary(df1$length_seq1_i) #to show the main information about the distribution of length *with intervals*

#barplots of the distribution of the length of prediction in the db_G0
bi1<-barplot(table(df1$length_seq1_i), xlab="Length of G1 database sequences in pb", ylab="Number of predictions")


```



# Plot with more intervals to have a better idea of what is the distribution in the interval [100:1000] for db_G0


```{r}

df0$length_seq0_ii<-cut(df0$length_seq0,c(0,100,300,500,700,1000,3000,5000,10000,30000,70000,100000, 300000),na.rm=TRUE,dig.lab = 10) #we cut more 

head(df0$length_seq0_i)
bi00<-barplot(table(df0$length_seq0_ii), xlab="Length of G0 database sequences in pb", ylab="Number of sequences") #new barplot with more intervals

summary(df0$length_seq0_ii) #to show the main information about the distribution of length *with more intervals*


```


# Plot with more intervals to have a better idea of what is the distribution in the interval [100:1000] for db_G1


```{r}
#same for db_G1
df1$length_seq1_ii<-cut(df1$length_seq1,c(0,100,300,500,700,1000,3000,5000,10000,30000,70000,100000, 300000),na.rm=TRUE,dig.lab = 10)

head(df1$length_seq1_i)
bi11<-barplot(table(df1$length_seq1_ii), xlab="Length of G1 database sequences in pb", ylab="Number of sequences") #bi11 with more intervals bi1 with some intervals

summary(df1$length_seq1_ii)


```








# To get one of the sequence with a length arround 40000 bp

```{r}
### /!\Quand j'ai fais mon 1er gg slides, dans les lignes en dessous j'avais mis seq0, df0 ... résultats surement à modifier... #### alors que s'occupe que de G1 à partir de là

#get all length of seq with length>=40K
plus_40k_length<-df1$length_seq1[df1$length_seq1 >= 40000]; plus_40k_length

# get all the ids of seq with length >=40K
plus_40k_idf<-df1$idf_seq1[df1$length_seq1 >= 40000]; plus_40k_idf

#sort by ascending values of length of seq >=40K
sort(plus_40k_length) #the smaller has a length of 43296 bp


#I have chosen the seq with a length of 43296 bp which corresponds to "RDN_A037_612"
pred_40k<-df1$idf_seq1[df1$length_seq1==43296];pred_40k # return the id with the length of 43 296 bp RDN_A037_612" 


# for the seq with a length of 43330 bp--> idf="RDN_D091_281"
pred2_40k<-df1$idf_seq1[df1$length_seq1==43330];pred2_40k


```




# To know which sequences corresponds to a value of length

# The largest prediction
```{r}

df1$idf_seq1[df1$length_seq1==214590] #the value of 214 590 was known with the summary above --> the id of the largest prediction is "RDN_D067_35"

```


# Get some predictions (with their id + length) in order to make a blast+ RepeatMasker to see what it is


```{r}
b<-df1$idf_seq1[ df1$length_seq1>700 & df1$length_seq1<1000];b #get all ids with an length >700 and <1000
b[500] #chose on among the liste--> the 500th--> The id returned is "RDN_A019_473"

df1$length_seq1[ df1$idf_seq1=="RDN_A019_473"] # to get it's length-->980 bp

```

## End of this script
