---
title: Analysis of the mapping of the prediction of aphid_TE_db_G1.ga to the sequence
  of Buchnera aphidicola reference genome
author: "Kamély Lumière"
date: "04/05/2023"
output: html_document
---

# Get the list_length of G1 to make a dataframe and use it for the analysis


```{r }

data_G1 <- read.table(file ="C:/Users/Anne-Flore/Desktop/klumiere/list-length_G1.txt", header = TRUE); data_G1 # get the data to make df
length_seq1<- data_G1[,2]; 
idf_seq1<-data_G1[,1]

df1<-data.frame(idf_seq1,length_seq1); df1 #make a df (like in the script before);
summary(df1) #have the main ifnormation about the distribution of aphid_TE_db_G1.db

```



# Get sizes of id prediction which map to Buchnera reference genome 


```{r}

#idf_mapping= id of prediction which map with Buchnera genome
#idf score bit is taken as a head / title of the columns, not a real ligne of the file 

idf_infos_mapping<- read.table(file ="C:/Users/Anne-Flore/Desktop/klum/Buchnera/mapping_Buchnera_vs_aphid_TE.txt", header = TRUE) #load the data by the path to the datafiles
#idf_infos_mapping
dim(idf_infos_mapping) #500 rows et 3 columns

#get only ids predictions from the files with ids, evalue and score of the blast
idf_mapping<-idf_infos_mapping [,1];#idf_mapping
#typeof(idf_mapping)
length(idf_mapping) #500 ids in total

idf_mapping[1] #it shows the first element of the list of ids of the mapping
head(idf_mapping) # show the first ids of the mapping
```


# Get the length of prediciton whitch map to the Buchnera refeence genome

```{r}


liste_length_mapping<-c()
for ( i in 1: length(idf_mapping)){
 liste_length_mapping<-append(liste_length_mapping,df1$length_seq1[ df1$idf_seq1==idf_mapping[i]])
}

print(liste_length_mapping) #display all the length of prediciction which map

#typeof(liste_length_mapping)
print(liste_length_mapping[2]) #display the 2nd element of the list

summary(liste_length_mapping) # display the main information about the length


```

# How many predictions which map to Bucnhera genome have a length > 10 000 bp ?


```{r}
#create a dataframe with ids+ length which map to Buchnera 
df_mapping_buchnera<-data.frame(idf_mapping,liste_length_mapping); df_mapping_buchnera


s<-df_mapping_buchnera$idf_mapping[df_mapping_buchnera$liste_length_mapping>10000];s # ids of predictions which map with a length >10 000
length(s) #19 prediciton with a length of 10 000 map to BUCHNERA genome--> represents arround 1/6 od the big size of the database


```

# To add ">" to the ids ... but was useless because for the awk command we have to remove the ">" but can be useful later --> don't deleate and keep "commenté" !

```{r}
id2<-idf_infos_mapping [,1];id2
#<-paste0(">",id2);id3
#récupère les id avc > et les mets dans un fichier texte
#write.table(id3,"C:/Users/Anne-Flore/Desktop/klum/Buchnera/id3.txt",row.names=F,col.names=F,quote=F,sep='\t') #export only the ids with ">" before of prediction which map in a file named "id3.txt"

```



# Get ids of predictions which map and put them in a file .txt in order to remove them from the database et count the predictions later


```{r}
write.table(idf_mapping,"C:/Users/Anne-Flore/Desktop/klum/Buchnera/id_rm.txt",row.names=F,col.names=F,quote=F,sep='\t') #id_rm.txt: file wit all the ids to remove from the db aphid_TE_db_G1.fa

```

# To complete tabs of "Mapping of TE predictions to Buchnera ..." in google slides of google drive stage_kamely_lumiere

```{r}
# "OLD INFORMATIONS" --> about the db aphid_TE_db_G1.fa
dim.data.frame(df1)
head( df1)

#nb of rex, ahm, rdn in the db aphid_TE_db_G1.fa (also verify by grep"Ahm" aphid_TE_db_G1.ga | wc -l in Linux terminal....)
ahm_idf<-df1$idf_seq1[substr(df1$idf_seq1[],1,3)=="Ahm"];length(ahm_idf) #95
rex_idf<-idf_seq1[substr(df1$idf_seq1[],1,3)=="REX"];length(rex_idf) #90931
rdn_idf<-idf_seq1[substr(df1$idf_seq1[],1,3)=="RDN"];length(rdn_idf) #14585

#len of rex, ahm, rdn
ahm_len<-df1$length_seq1[substr(df1$idf_seq1[],1,3)=="Ahm"];ahm_len
min(ahm_len) #1132

rex_len<-df1$length_seq1[substr(df1$idf_seq1[],1,3)=="REX"];rex_len
min(rex_len) #76
max(rex_len) #9578

rdn_len<-df1$length_seq1[substr(df1$idf_seq1[],1,3)=="RDN"];rdn_len
min(rdn_len) #100
max(rdn_len) #214590

```


# Infos about the predictions mapping to the Buchnera genome

```{r}

ahm_idf_b<-df_mapping_buchnera$idf_mapping[substr(df_mapping_buchnera$idf_mapping[],1,3)=="Ahm"];length(ahm_idf_b) # 0: It's normal, there are no Ahmad2021 in the blast
rex_idf_b<-df_mapping_buchnera$idf_mapping[substr(df_mapping_buchnera$idf_mapping[],1,3)=="REX"];length(rex_idf_b) #479
rdn_idf_b<-df_mapping_buchnera$idf_mapping[substr(df_mapping_buchnera$idf_mapping[],1,3)=="RDN"];length(rdn_idf_b) #21


ahm_len_b<-df_mapping_buchnera$liste_length_mapping[substr(df_mapping_buchnera$idf_mapping,1,3)=="Ahm"];ahm_len_b # 0: normal
min(ahm_len_b)

rex_len_b<-df_mapping_buchnera$liste_length_mapping[substr(df_mapping_buchnera$idf_mapping,1,3)=="REX"];rex_len_b
min(rex_len_b) #820
max(rex_len_b) #7249

rdn_len_b<-df_mapping_buchnera$liste_length_mapping[substr(df_mapping_buchnera$idf_mapping,1,3)=="RDN"];rdn_len_b
min(rdn_len_b) #1892
max(rdn_len_b) #214590 

min(df_mapping_buchnera$liste_length_mapping)
max(df_mapping_buchnera$liste_length_mapping)


```


## End of the script